Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-19 sections/02-notation.tex
Update on Overleaf.

All the measures discussed, regardless of the area, have in common that the comparison and evaluation of the methods take into account the local absolute differences in different ways but do not directly consider whether the correct direction of change is issued
To our best knowledge, there is no work in the literature that addresses the trending capability of measurement series or predictions with continuous outcomes.
Because of the different ways in which data are generated and processed depending on the area of application, the data collected should be prepared in different ways for further processing in order to identify the trending ability (see Section~\ref{sec:trending}). \todo{Vielleicht nochmal Praxisbezug herausstellen, warum es sinnvoll ist, die Differenzen so zu formulieren?}
In particular, the following shows how the time series of change (with lag $l$) should be defined, depending on whether measurement, forecasting, or nowcasting methods are considered. For measurement:
\begin{equation}
    \diffxl = (x_{t+l} -x_{t})^T_{t=0} \label{eq:diffxl_measure}
\end{equation}
For forecasting and nowcasting bezeichnen wir mit y die wahren werte der quantity of interesst. For Forcasting ist der Werzum Zeitpu
\begin{equation}
    \diffxl = (x_{t,t+l} -y_{t})^T_{t=0} \label{eq:diffxl_forecasting}
\end{equation}
For nowcasting:
\begin{equation}
\diffxl = 
\begin{cases} 
(x_{t,t+l} -x_{t,t})^T_{t=0} & \text{if } y_{t} \text{ is not known at time } t, \\
(x_{t,t+l} -y_{t})^T_{t=0}  & \text{else}.
\end{cases} \label{eq:diffxl_nowcasting}
\end{equation}

>>>>

All the measures discussed, regardless of the area, have in common that the comparison and evaluation of the methods take into account the local absolute differences in different ways but do not directly consider whether the correct direction of change is issued.
Because of the different ways in which data are generated and processed depending on the area of application, the data collected should be prepared in different ways for further processing in order to identify the trending ability (see Section~\ref{sec:trending}). \todo{Vielleicht nochmal Praxisbezug herausstellen, warum es sinnvoll ist, die Differenzen so zu formulieren?}
In particular, the following shows how the time series of change (with lag $l$) should be defined, depending on whether measurement, forecasting, or nowcasting methods are considered. For measurement:
\begin{equation}
    \diffxl = (x_{t+l} -x_{t})^T_{t=0} \label{eq:diffxl_measure}
\end{equation}
For forecasts and nowcasts, we use $(\mathbf{y})^T_{t=0}$ to denote the true values of the quantity of interest. For forecasts, the current value is known at the time of the forecast, so a forecast for the time $t+l$ means the prediction of a change $x_{t,t+l} -y_{t}$ between $t$ and $t+l$. The time series of change can therefore be defined as follows 
\begin{equation}
    \diffxl = (x_{t,t+l} -y_{t})^T_{t=0}.\label{eq:diffxl_forecasting}
\end{equation}
For nowcasting muss der Wert des aktuellen Zeitpunktes zum Vorhersage-Zeitpunkt nicht beaknnt sein. Dies kann durch folgende Fall Unterscheidung berücjksichtig werden:
\begin{equation}
\diffxl = 
\begin{cases} 
(x_{t,t+l} -x_{t,t})^T_{t=0} & \text{if } y_{t} \text{ is not known at time } t, \\
(x_{t,t+l} -y_{t})^T_{t=0}  & \text{else}.
\end{cases} \label{eq:diffxl_nowcasting}
\end{equation}
